Towards Cloud Bursting for Extreme Scale Supercomputers

### 2014-06-26 paper/paper.tex
0625

\documentclass[JIP,draft]{ipsj}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{verbatim}

\bibliographystyle{ipsjunsrt-e.bst}

@@

%supercomputers usually consist of a large number of nodes, provide high parallelism for multi-user.
%However computing nodes in supercomputers will not meet the request in some situation, such as some nodes have to be shutted down to reduce electric consumption in summer or just several serial applications occupy nodes making others must wait.
%large serial applications will occupy computation nodes for a long time and causes some other applications which use numerous nodes to wait in a running queue, leads a low utilization of computing resource.
%One solution is running virtual machine on 
%In this paper, a comparision was made between a Public Cloud (AMAZON EC2) and a Supercomputer (TSUBAME) on Ethernet Performance and leading a 
%In order to satisfy these temporary request peak, we are trying to federate supercomputers with public cloud, which is known as cloud bursting.
%Although some sophisticated solutions are available, still we are facing several challenges, since there are a significant performance gap between supercomputers and public cloud.
%In this paper, we focus on I/O throughput between these two environments, we propose a I/O Bursting Buffer Model to burst I/O throughput between supercomputer and public cloud and reduce the cost for extra time usage caused by low I/O throughput.
%we also provide a simulation based on several benchmarks on TSUBAME supercomputer and AMAZON EC2 public cloud.
%The result shows our model can provide a stable and high I/O throughput as well as a low cost in most cases.

@@

%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until perious job finished although there are 49 nodes remainning available.
%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
Another problem is the power problem in summer, in order to reduce power comsumation, some nodes will be forced to be shutted down, reducing numbers of nodes will make the first problem more serous.

One solution is federating supercomputer with a public cloud, moving parts of job and computation to public cloud when there are not enough computing nodes available for user's request, which is known as cloud bursting.
Although cloud bursting is used by several companies and already have some sophisticated solutions\cite{Eucalyptus,stratos,Seagull}, since there are a significant performance gap between supercomputer nodes and cloud nodes, there will still be several problems when we try to ferderate a supercomputer with a public cloud, and there are several studies on .
The biggest problem will be data transfer throughput between two environment, supercomputers usual deal with Gigabyte or even Petabyte input and output of data, low I/O throughput will suffer supercomputer user. This paper focuses on methodology of increasing throughput when we do federation.

In order to increase data transfer throughput, we propose a I/O bursting buffer architecture that uses several nodes in each cloud as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O bursting buffer model that uses to switch between I/O bursting buffer mode and direct connect mode.
%This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
%Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
Also, public cloud usually charges for nodes usage, using I/O bursting buffer may reduce the computation time, but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.

Our contribution can be summary as following:
\begin{itemize}
	\item An architecture of I/O bursting buffer for increasing data transfer throughput between two clouds.
	\item A throughput-based I/O bursting buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two clouds, and a cost-based I/O bursting buffer model uses to reduce the total cost.
	%\item 
	\item Evaluating I/O bursting buffer architecture and two models by using data obtained from several benchmarks from tsubame supercomputer and AMAZON EC2 public cloud.
\end{itemize}
%2
The remainder of this paper is orginized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2 
will be shown in section 5, and finally, conclusion and related work will be seen in section 6.

@@

%When people analyze large size of data, parallel programme is widely used in order to reduce computation time, especially when using supercomputer.
%However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
%Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, causing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
%Consider following situation, there are 50 nodes available when a user submits a serial program using 1 node for 4 hours, after an hour a user try to run a program using 50 nodes, then he can't start his program until the first user finished his job.
%Such situation happens frequently when thousands and hundreds of users using one system at the same time and leading a low utilization of computing resource.
%One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer, but sometime it still can't meet the request.
%For request not always reaches peak, it is not wise to increase nodes just for a temporary request peak.
%However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shutted down to reduce electricity consumption in the case of TSUBAME Supercomputer.
%Facing these problems, one solution will be federate supercomputer with public cloud.
%By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
%Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.

%Data shown in this section is taken from AMAZON EC2 m3.medium nodes, which have 3.75GiB memory and Moderate Network Performance and TSUBAME 2.5 V queue, which uses VM.
\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{point_to_point_lab}
	%\includegraphics{}
	\caption{I/O Throughput to Lustre inside TSUBAME direct mount}
	\label{throughput TSUBAME}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{point_to_point_lab}
	%\includegraphics{}
	\caption{I/O Throughput from AMAZON EC2 to file system inside our lab using sshfs}
	\label{throughput AMAZON to MATSULAB}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{point_to_point_AMAZON}
	%\includegraphics{}
	\caption{point to point connection inside AMAZON}
	\label{point to point connection AMAZON}
\end{figure}

@@

As we know, throughput gap between innerconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
We use Iperf\cite{iperf}, which was developed by NLANR/DAST as a modern alternative for measuring TCP and UDP bandwidth performance, and IOR\cite{IOR}, which is widely used for benchmarking parallel file systems using POSIX, MPIIO, or HDF5 interfaces.

Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a innerconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggreate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
On the other hand, Fig.~\ref{throughput AMAZON to MATSULAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access.
Since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from AMAZON.
We can see that the I/O throughput also grows as number of nodes grows but the aggreate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of innerconnection inside supercomputer is quit larger than that from AMAZON.
%Also, if we compare the one nodes I/O throughput, 
If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.

%But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the innerconnection throughput 
However, if we consider innerconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, figure shows a perfect linar line also a strong scalability.
Since we can achieve a high innerconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.

Although there are some studies about workflow optimization and  balance\cite{Workload}, Since data transfer rate is extremely low in Internet compared with innerconnection network and data size processed is extremely large, user do not want to settle their nodes across two systems, so in this model, we just consider the situation that all nodes used for the same job are settled in the same system.

@@

An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be tranferred to final storage system.
%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.

@@

%Migration operation occurs when some nodes have to be shutted down in one cloud 
%all jobs running on these nodes have to be backed up by using snapshot,

@@

%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assgined only  and I/O burst buffer nodes, which assigned both private IP address.

@@

When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O data will be transferred to I/O burst buffer.
First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are settled in the same system, so data consistency can be guaranteed since that.
Buffer queue operation includeing data write back and operation when queue is full will be described in following section.

When user issue a read request, there are two conditions: file is bufferred in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.

Fig.~\ref{overview} shows a overall illustrate of I/O burst buffer architecture:

Consider there are two systems, named system 1 and system 2, and we assume that 
%Arrows stand for network connection.
%Orange arrows are innerconnection networks inside cloud, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
%Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud. 
%Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.

@@

%For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation. 
\subsection{Buffer Queue Write Back}

in this subsection, we introduce operation of buffer queue

@@

In this section we describe operations when file is not in I/O buffer nodes or file needs to be write back to storage in another system.
We propose two kindes of model: one-side buffer and two-side buffer.

@@

As Fig.~\ref{read and write} blue arrow shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
When I/O nodes need to write data back to storage in system 1, since data is already spread among I/O nodes, a parallel write can be achieve to fully utilize the Internet bandwidth.

%data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
%After reading finished, I/O buffer nodes send data to each computing node Simultaneously, there data will be restructure by using protocol described below.

@@

@@

As Fig.~\ref{index protocol} shows, two indexs are used in this protocol: main index and sub-index.
There are two phases of data splitting in both reading and writing operation, 
\end{comment}
%\subsubsection{Node Migration}
%Node migration happens when some nodes have to be shutted down due to some situation like power problem in summer, and still need to provide service to users.
%In these cases, nodes will be migrate by snapshot, usually snapshots of these nodes will first be stored into shared storage, then these snapshots will be transferred to another cloud, and start VM by using these snapshots.

@@

\section{I/O Bursting Buffer Model}

@@

Throughput-based Model and Cost-based Model will be described in this section.
We make following definitions in order to describe our model:

\begin{itemize}
	\item Numbers of computing nodes are $c_1,c_2$, and numbers of I/O buffer nodes are $n_1, n_2$ respectively.
	\item $D_1(n_2)$ is throughput when $n_2$ I/O nodes in sytem 1 connect to storage in system 2 directly, similar to $D_1(n_2)$, $D_2(n_1)$ refers to throughput when $n_1$ I/O nodes in cloud 2 connect to storage in cloud 1 directly, here we assume only I/O nodes in each system have Internet connection.
	\item Since overall Internet throughput is affected by number of nodes involved in connection. $I(n_1,n_2)$ is used to refer to Internet throughput using $n_1,n_2$ I/O buffer nodes respectively.
	\item For interconnection network throughput, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
	\item $M_1(n_1),M_2(n_2)$ are throughput of connection between storage and $n_1$ I/O nodes in system 1 and ,storage and $n_2$ I/O nodes in system 2.
	\item Cost for standard node in system 1 is defined as $C_1\_Money(T)$ for $T$ time usage and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, here cost for I/O nodes is defined as $C_1\_High\_Money(T),C_2\_High\_Money(T)$ for $T$ time respectively.
	\item Available 
\end{itemize}

\subsection{Throughput-based Model}
%There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
When I/O buffer nodes in cloud 2 connect to storage in cloud 1, there are two data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to storage in cloud 1, so throughput will be:

\begin{equation}
	\text{throughput}_{\text{direct}}=\min\{D_1(n_2),E_2(n_2)\} \label{throughput1}
\end{equation}

In the case of using I/O buffer nodes in both cloud, there are three data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to I/O buffer nodes in cloud 1, I/O buffer nodes in cloud 1 to storage in cloud 1, throughput will be:

>>>>

\documentclass[JIP,draft]{ipsj}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{supertabular}
\bibliographystyle{ipsjunsrt-e.bst}

@@

%supercomputers usually consist of a large number of nodes, provide high parallelism for multi-user.
%However computing nodes in supercomputers will not meet the request in some situation, such as some nodes have to be shut down to reduce electric consumption in summer or just several serial applications occupy nodes making others must wait.
%large serial applications will occupy computation nodes for a long time and causes some other applications which use numerous nodes to wait in a running queue, leads a low utilization of computing resource.
%One solution is running virtual machine on 
%In this paper, a comparison was made between a Public Cloud (AMAZON EC2) and a Supercomputer (TSUBAME) on Ethernet Performance and leading a 
%In order to satisfy these temporary request peak, we are trying to federate supercomputers with public cloud, which is known as cloud bursting.
%Although some sophisticated solutions are available, still we are facing several challenges, since there are a significant performance gap between supercomputers and public cloud.
%In this paper, we focus on I/O throughput between these two environments, we propose a I/O Bursting Buffer Model to burst I/O throughput between supercomputer and public cloud and reduce the cost for extra time usage caused by low I/O throughput.
%we also provide a simulation based on several benchmarks on TSUBAME supercomputer and AMAZON EC2 public cloud.
%The result shows our model can provide a stable and high I/O throughput as well as a low cost in most cases.

@@

%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until previous job finished although there are 49 nodes remainning available.
%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
Another problem is the power problem in summer, in order to reduce power consumption, some nodes will be forced to be shut down, reducing numbers of nodes will make the first problem more serous.

One solution is federating supercomputer with a public cloud, moving parts of job and computation to public cloud when there are not enough computing nodes available for user's request, which is known as cloud bursting.
Although cloud bursting is used by several companies and already have some sophisticated solutions\cite{Eucalyptus,stratos,Seagull}, since there are a significant performance gap between supercomputer nodes and cloud nodes, there will still be several problems when we try to federate a supercomputer with a public cloud, and there are several studies on cloud burst about cost\cite{Seagull}, execution time\cite{time_and_cost}, etc..
The biggest problem will be data transfer throughput between two environment, supercomputers usual deal with Gigabyte or even Petabyte input and output of data, low I/O throughput will suffer supercomputer user. This paper focuses on methodology of increasing throughput when we do federation.

In order to increase data transfer throughput, we propose a I/O burst buffer architecture that uses several nodes in each system as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O burst buffer model that uses to switch between I/O burst buffer mode and direct connect mode.
%This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
%Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
Also, public cloud usually charges for nodes usage, using I/O bursting buffer may reduce the computation time, but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.

Our contribution can be summary as following:
\begin{itemize}
	\item An architecture of I/O burst buffer for increasing data transfer throughput between two systems.
	\item A throughput-based I/O burst buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two systems, a cost-based I/O burst buffer model uses to reduce the total cost and a queue model used.
	%\item 
	\item Evaluating I/O burst buffer architecture and two models by using data obtained from several benchmarks from TSUBAME supercomputer and AMAZON EC2 public cloud.
\end{itemize}
%2
The remainder of this paper is organized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2 
will be shown in section 5, and finally, conclusion and related work will be seen in section 6.

@@

%When people analyze large size of data, parallel programme is widely used in order to reduce computation time, especially when using supercomputer.
%However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
%Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, causing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
%Consider following situation, there are 50 nodes available when a user submits a serial program using 1 node for 4 hours, after an hour a user try to run a program using 50 nodes, then he can't start his program until the first user finished his job.
%Such situation happens frequently when thousands and hundreds of users using one system at the same time and leading a low utilization of computing resource.
%One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer, but sometime it still can't meet the request.
%For request not always reaches peak, it is not wise to increase nodes just for a temporary request peak.
%However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shut down to reduce electricity consumption in the case of TSUBAME Supercomputer.
%Facing these problems, one solution will be federate supercomputer with public cloud.
%By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
%Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.

%Data shown in this section is taken from AMAZON EC2 m3.medium nodes, which have 3.75GiB memory and Moderate Network Performance and TSUBAME 2.5 V queue, which uses VM.
\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{throughput_tsubame}
	\caption{I/O Throughput to Lustre inside TSUBAME direct mount}
	\label{throughput TSUBAME}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{AMAZON_to_OUR_LAB}
	\caption{I/O Throughput from AMAZON EC2 to file system inside our lab using sshfs}
	\label{throughput AMAZON to OURLAB}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{point_to_point_AMAZON}
	\caption{point to point connection inside AMAZON}
	\label{point to point connection AMAZON}
\end{figure}

@@

As we know, throughput gap between interconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
We use Iperf\cite{iperf}, which was developed by NLANR/DAST as a modern alternative for measuring TCP and UDP bandwidth performance, and IOR\cite{IOR}, which is widely used for benchmarking parallel file systems using POSIX, MPIIO, or HDF5 interfaces.

Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access.
Since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from AMAZON.
We can see that the I/O throughput also grows as number of nodes grows but the aggregate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of interconnection inside supercomputer is quit larger than that from AMAZON.
%Also, if we compare the one nodes I/O throughput, 
Also if we compare Fig.~\ref{point to point connection LAB} with Fig.~\ref{throughput AMAZON to OURLAB}, the maximum throughput 
If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.

%But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the interconnection throughput 
However, if we consider interconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
Since we can achieve a high interconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.

Although there are some studies about workflow optimization and  balance\cite{Workload}, Since data transfer rate is extremely low in Internet compared with interconnection network and data size processed is extremely large, user do not want to settle their nodes across two systems, so in this model, we just consider the situation that all nodes used for the same job are allocated in the same system.

@@

An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be transferred to final storage system.
%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.

@@

%Migration operation occurs when some nodes have to be shut down in one cloud 
%all jobs running on these nodes have to be backed up by using snapshot,

@@

%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assigned only  and I/O burst buffer nodes, which assigned both private IP address.

@@

When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O data will be transferred to I/O burst buffer.
First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are allocated in the same system, so data consistency can be guaranteed since that.
Buffer queue operation including data write back and operation when queue is full will be described in following section.

When user issue a read request, there are two conditions: file is buffered in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.

Fig.~\ref{overview} shows a overall illustrate of I/O burst buffer architecture.

%Consider there are two systems, named system 1 and system 2

%Arrows stand for network connection.
%Orange arrows are interconnection networks inside cloud, although two clouds used the same color for interconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
%Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud. 
%Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.

@@

%For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation.

%in this subsection, we introduce operations of buffer queue write back.

@@

In this section we describe operations when file is not in I/O buffer nodes or file needs to be write back to storage in another system.
We propose two kinds of model: one-side buffer and two-side buffer.

@@

As Fig.~\ref{read and write} blue arrow shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
When I/O nodes need to write data back to storage in another system, since data is already spread among I/O nodes, a parallel write can be achieve to fully utilize the Internet bandwidth.

Similarly, when I/O nodes need to read data from storage in another system, several I/O nodes will be assigned equal size of data, and then these nodes read assigned piece of data from the storage concurrently.

There will be two problems in this solution:
\begin{itemize}
	\item First storage should be opened to Internet, in order that I/O nodes can read from or write to it.
		However storage system in supercomputer store Petabyte of research data, open the access of storage system means that put these research data under risk of attack.
	\item As we mentioned before, throughput of one side communication is lower than two side communication, since we use SSH protocol based File system for security reason.
		also two side communication can achieve a higher throughput with fewer nodes, according to pay-as-you-go policy, reduce number of nodes can reduce cost.
\end{itemize}
%data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
%After reading finished, I/O buffer nodes send data to each computing node Simultaneously, there data will be restructure by using protocol described below.

@@

On the contrary, two-side buffer solution use I/O buffer nodes in both two systems as Fig.~\ref{read and write} orange arrows show.
I/O data will be split twice, transferred throughput two sides of I/O buffer nodes and then reached the destination.

Consider I/O nodes in system 2 issue a write back operation, also, data is already spread among I/O nodes in system 2, each I/O node will find a pair among I/O nodes in system 1, then transfer their piece of data to system 1 concurrently.
After I/O node in system 1 received data, they write data back to storage in system 1.

Compared with one-side buffer, two-side buffer required one more data transfer (I/O nodes to storage in the same system), if storage data transfer throuhput become a bottleneck, two-side buffer will cost more time than one-side buffer.
Also, two-side buffer require both systems allocate I/O buffer nodes, if node usage is charge in both system, total cost may be larger than one-side buffer.

%the bottleneck is still Internet throughput, since interconnection is far faster than Internet.
Since two-side buffer does not read data from or write data to storage directly, it means we can compress data before transfer it, though it will take some time to compress and decompress data, when the Internet throughput is extremely low, compress and decompress time will be far smaller than tranferring time, and compress data can make more data buffered in buffer queue.
Also, unlike one-side buffer, two-side buffer do not require storage to be opened to Internet, only required several I/O nodes have access to Internet.

@@

As Fig.~\ref{index protocol} shows, two indexs are used in this protocol: main index and sub-index.
There are two phases of data splitting in both reading and writing operation, 
\end{comment}
%\subsubsection{Node Migration}
%Node migration happens when some nodes have to be shut down due to some situation like power problem in summer, and still need to provide service to users.
%In these cases, nodes will be migrate by snapshot, usually snapshots of these nodes will first be stored into shared storage, then these snapshots will be transferred to another cloud, and start VM by using these snapshots.

@@

\section{I/O Burst Buffer Model}

@@

Throughput-based Model, Cost-based Model and buffer queue write back model will be described in this section.
Throughput-based Model compare one-side buffer throughput with two-side buffer, cost-based model compare one-side buffer cost with two-side buffer, and buffer queue write back model. 
We make definitions shows in Table.~\ref{definition} in order to describe our model:
\begin{table}[tb]
	\caption{Definition of parameters}
	\label{definition}
\begin{tabular}{|p{3cm}|p{5cm}|}
	\hline
	$c_1,c_2$&Numbers of computing nodes in system 1 and system 2\\\hline
	$n_1, n_2$&Numbers of I/O buffer nodes in system 1 and system 2.\\\hline
	$m_1,m_2$&Available memory size for each I/O node in system 1 and 2, also the maximum buffer size will be $n_1\times m_1$ and $n_2\times m_2$\\\hline
	$D_1(n_2),D_2(n_2)$&Throughput when $n_2$($n_1$) I/O nodes in system 1 (system 2) connect to storage in the other system directly, here we assume only I/O nodes in each system have Internet connection.\\\hline
	$I(n_1,n_2)$& 	Internet throughput using $n_1,n_2$ I/O buffer nodes respectively, Since overall Internet throughput is affected by number of nodes involved in connection.\\\hline
	$E_1(n_1), E_2(n_2)$&Interconnection network throughput in system 1 and 2, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes.\\\hline
	%, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
	$M_1(n_1),M_2(n_2)$& Throughput of connection between storage and $n_1$ I/O nodes in system 1 and storage and $n_2$ I/O nodes in system 2.\\\hline
	$C_1\_Money(T)$,$C_2\_Money(T)$& Cost for standard node in system 1 and 2 for $T$ time usage\\\hline
	%and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, 
	$C_1\_High\_Money(T)$,$C_2\_High\_Money(T)$& cost I/O nodes in system 1 and 2 for $T$ time usage, since I/O nodes may use a better network condition, we assume it will cost more than normal nodes.\\\hline
\end{tabular}
\end{table}
